Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization

### 2019-04-10 WRITEUP/ms.tex

\begin{figure*}
\centering
\includegraphics[width=\textwidth]{\figpath/alpha_vir_ss21-ss22.png}
\caption{$\alpha_{\rm vir}$-mass relation for pre-starburst (left) and starburst phase. 
Definition of the symbol shown are the same as in \Fig{larsons_single}.
Blue star symbols show gas-only $\alpha_{\rm vir}$ and blue circulate dots show total $\alpha_{\rm vir, tot}$ of MCCs in \flower. 
\label{fig:alpha21-22}}
\end{figure*}

@@

% Starburst 
In the starburst phase, MCCs have velocity dispersion, sizes,
and virial parameter comparable to those in the accreting phase; however, the MCCs in the starburst phase span 
a wider range in $\sigma^2/R$ and gas surface density. 
Due to a time delay between cloud collapse and \SF, we also examine the virial parameter of MCCs in the pre-starburst phase. 
As shown in \Fig{alpha21-22}, the total virial parameter (blue dots in the figure) 
of a subset of MCCs in the pre-starburst phase are lower than those in the starburst phase of the same mass range. which is as expected.
% None of these MCCs are in the unstable regime ($alpha_{\rm vir} < 2$) because the MCCs are not directly the collapsing structures, 
% i.e., we haven’t reached those scales where true collapse is happening. 
% This implication of this is that to examine the truly star-forming structures (cores) will require resolution smaller than ~40 pc.

@@

\DL{
1) Note becasuse some MCCs have high stellar-to-gas mass ratios, we plot both gas-only virial parameter 
and the total virial parameter (eqn xx) on the alphavir-mass plots in \Fig{}. The former is used in \obs since 
the quantities are measured using gas tracers. On the other hand, because our MCs are identified with gas density and 
some have high stellar-to-gas mass ratio, influence from the stellar component plays a non-negligible role, as seen in Toomre Q analysis.
% 
2) TODO: Add a plot showing the different alphavir over time. Add a line somewhere that feedback plays in important role in the virial parameter, as 
can be seen in the strong variation in alphavir across the different evolutionary stages of \flower. 
% 
3) add alphavir versus stellar-to-gas mass ratio, 
which shows in the pre-SB phase, we see overall lower alphavir. 
We interpret the alphavir versus stellar-to-gas mass ratio plot as 
1) the general trend is consistent with physics -- alphavir of MCCs are lower compared to other snapshots in the pre-SB phase.  
The reason that we don’t see any MCCs with alphavir $<$ 2 can be understood by realizing that the MCCs are not 
directly the collapsing structures, i.e., we haven’t reached those scales where true collapse is happening.
This implication of this is that to examine the truly star-forming structures (cores) will require resolution smaller than ~40 pc.
}

@@

Excluding the biggest MCC identified in each evolutionary stage (i.e., the top right cluster of points in the 
linewidth-size relation of \Fig{larsons_single} and the top left panel of \Fig{alpha16-28}), which correspond to 
mostly the main disk of \flower.......{\DL blah}.
The MCCs of \flower have dynamics largely similar to those observed in
$z$\ssim2 spatially resolved studies of gas-rich star-forming
galaxies, in terms of their velocity dispersions, sizes, and gas
surface densities (\Fig{larsons_single}; see e.g.,
\citealt{Swinbank11a}), with sizes of the order of $R\simeq$\,100\,pc
and velocity dispersions of $\sigma\simeq$\,20$-$80\,\kms. 
\MM{They agree in $\sigma$ vs.\ $R$, but their virial parameters seem
  high compared to the data sets provided, particularly for their
  relatively low surface densities (Figs.\ 5, 6).}
%
% velocity dispersion, larsons
%
Their velocity dispersions are also comparable to those observed in the inner Milky way and nearby gas-rich galaxies (e.g., M64; \citealt{Oka01a, Rosolowsky05a, Heyer09a}), which lies along the locus of $\sigma\propto R^{0.56}$. Such high velocity dispersions and surface densities are expected since they are located in the nuclear regions of the galaxy, where the potential well is also deep. The higher velocity dispersions
(see footnote~\ref{ftn:veldisp} on page \pageref{ftn:veldisp}) of
these MCCs can also be understood as they have experienced more recent
episodes of \SF as \flower is assembling its stellar mass (these MCCs
also have higher stellar-to-gas mass ratios of $\sim$60). \MM{This is
  an enormous stellar to gas mass ratio, suggesting the clouds are
  completely controlled by the gravitational potential of the stars.
h  A normal molecular cloud would have a ratio of < 0.1!  The
  implications of this for the apparent virial parameters and velocity
dispersions need to be considered much more carefully than they have been.}
%
In fact, by the accreting stage (see \Fig{SFH}a) at $z\simeq$\,7.2, 
\flower has assembled a stellar mass of
$M_\star$\eq7.5\E{9}\,\Msun. Thus, the higher velocity dispersion is
due in part to the stronger stellar feedback \MM{Again, not clear that
  this is feedback and not potential driven. Can you demonstrate one
  or the other explicitly?} compared to e.g., MCCs in
its satellites ($\sigma\simeq$10\,\kms) \MM{This needs to be shown in
  a Figure, not just asserted}.

>>>>

\begin{figure*}
% \centering
\includegraphics[width=\textwidth]{\figpath/alpha_vir_ss21-ss22.png}
% \includegraphics[width=0.925\textwidth]{\figpath/alpha_vir-stellar_to_gas_ss21-ss22.png}
\caption{
% Top: 
Virial parameter and mass of MCCs in the pre-starburst (left) and starburst phase (right) of \flower. 
% Bottom: $\alpha_{\rm vir}$ and stellar-to-gas mass ratio of MCCs.
Definition of the symbol shown are the same as in \Fig{larsons_single}.
Blue star symbols show gas-only $\alpha_{\rm vir}$ and blue circulate dots show total $\alpha_{\rm vir, tot}$ of MCCs in \flower. 
Excluding the biggest MCCs, MCCs in the pre-starburst phase have a lower $\alpha_{\rm vir}$ compared to the starburst phase. 
% Overall, the stellar-to-gas mass ratio of MCCs in the starburst phase is higher. 
\label{fig:alpha21-22}}
\end{figure*}

\begin{figure}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=0.5\textwidth]{\figpath/Mach_pressure-stellar-to-gas_ss21-ss27.png}
\caption{
Mach number derived from the pressure of MCCs as a function of their stellar-to-gas mass ratio in four evolutionary stages, as denoted in the panels.
% ss20,21,22,27
The Mach number of MCCs with $M_\star/M_{\rm cl} \simeq 0.1 - 1$ increases as \SF proceed in \flower. In that bottom panel, the 
light blue symbols correspond to MCCs in the satellites in the outskirt of \flower and are identified with low $n_{\rm cut}$.
\label{fig:Mach_stellarRatio}}
\end{figure}

@@

% Starburst 
In the starburst phase, MCCs have velocity dispersion, sizes,
and virial parameter comparable to those in the accreting phase; however, the MCCs in the starburst phase span 
a wider range in $\sigma^2/R$ and gas surface density. 
Due to a time delay between cloud collapse and \SF, we also examine the virial parameter of MCCs in the pre-starburst phase. 
As shown in \Fig{alpha21-22}, the total virial parameter (blue dots in the figure) 
of a subset of MCCs in the pre-starburst phase are lower than those in the starburst phase of the same mass range, which is as expected.
%Similarly, the stellar-to-gas mass ratio of MCCs in the starburst phase is higher overall (see bottom panels of \Fig{alpha21-22}).
%These trends are as expected in the MCC properties prior to and during a starburst. 
% None of these MCCs are in the unstable regime ($alpha_{\rm vir} < 2$) because the MCCs are not directly the collapsing structures, 
% i.e., we haven’t reached those scales where true collapse is happening. 
% This implication of this is that to examine the truly star-forming structures (cores) will require resolution smaller than ~40 pc.
As \SF proceed, stellar feedback inject kinetic energy in the form of turbulence. As shown in 
\Fig{Mach_stellarRatio}, the Mach number of MCCs with a stellar-to-gas mass ratio of $M_\star/M_{\rm gas} \simeq 0.1 - 1$ 
(i.e., excluding the main component of \flower with $M_\star/M_{\rm gas} \gtrsim 1$; see e.g., \Fig{stellarRatio16})
increases from the pre-starburst phase through the post-starburst phase.

@@

\DL{
1) Add to discussion in Sec 6.3? As shown in alphavir total, the high stellar-to-gas mass ratio, 
influence from the stellar component plays a non-negligible role, as seen in Toomre Q analysis.
% 
2) TODO: Add a plot showing the different alphavir over time. Add a line somewhere that feedback plays in important role in the virial parameter, as 
can be seen in the strong variation in alphavir across the different evolutionary stages of \flower. 
and also the increase in $M$ as \SF proceed in \flower, see \Fig{Mach_stellarRatio}.
% 
3) overall lower alphavir in the pre-SB phase in \Fig{alpha21-22}. 
1) the general trend is consistent with physics -- alphavir of MCCs are lower compared to other snapshots in the pre-SB phase.  
The reason that we don’t see any MCCs with alphavir $<$ 2 can be understood by realizing that the MCCs are not 
directly the collapsing structures, i.e., we haven’t reached those scales where true collapse is happening.
This implication of this is that to examine the truly star-forming structures (cores) will require resolution smaller than ~40 pc.
}

@@

Excluding the biggest MCC identified in each evolutionary stage (i.e., the top right cluster of points in the 
linewidth-size relation of \Fig{larsons_single} and the top left panel of \Fig{alpha16-28}), which correspond to 
the main disk of \flower, the MCCs of \flower have dynamics largely similar to those observed in
$z$\ssim2 spatially resolved studies of gas-rich star-forming
galaxies, in terms of their velocity dispersions, sizes, and gas
surface densities (\Fig{larsons_single}; see e.g.,
\citealt{Swinbank11a}), with sizes of the order of $R\simeq$\,100\,pc
and velocity dispersions of $\sigma\simeq$\,20$-$80\,\kms. 
Their velocity dispersions are also comparable to those observed in the inner Milky way and nearby gas-rich galaxies (e.g., M64; \citealt{Oka01a, Rosolowsky05a, Heyer09a}), which lies along the locus of $\sigma\propto R^{0.56}$. Such high velocity dispersions and surface densities are expected since they are located in the nuclear regions of the galaxy, where the potential well is also deep. The higher velocity dispersions
(see footnote~\ref{ftn:veldisp} on page \pageref{ftn:veldisp}) of
these MCCs can also be understood as they have experienced more recent
episodes of \SF as \flower is assembling its stellar mass --- these MCCs have higher stellar-to-gas mass ratios of $M_\star/M_{\rm gas}\simeq0.1 - 1$ (\Fig{stellarRatio16}) and high turbulent pressure as shown by the high $\mathcal{M}$ in \Fig{Mach_stellarRatio}.  
%
In fact, by the accreting stage (see \Fig{SFH}a) at $z\simeq$\,7.2, 
\flower has assembled a stellar mass of
$M_\star$\eq7.5\E{9}\,\Msun. Thus, the higher velocity dispersion is
due in part to the stronger stellar feedback \MM{Again, not clear that
  this is feedback and not potential driven. Can you demonstrate one
  or the other explicitly?}
